\singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant floral and reproductive traits determine interactions with floral visitors

### 2021-08-14 Draft/Manuscript.tex
edits

\leavevmode\hypertarget{ref-tur2013}{}%
14. Tur, C., Castro-Urgal, R. \& Traveset, A. Linking Plant Specialization to Dependence in Interactions for Seed Set in Pollination Networks. \emph{PLoS ONE} \textbf{8}, e78294 (2013).

@@

\leavevmode\hypertarget{ref-barrett2003}{}%
23. Barrett, S. C. H. Mating strategies in flowering plants: The outcrossing-selfing paradigm and beyond. \emph{Philos. Trans. R. Soc. Lond., B, Biol. Sci.} \textbf{358}, 991--1004 (2003).

@@

\leavevmode\hypertarget{ref-bartomeus2013}{}%
27. Bartomeus, I. Understanding Linkage Rules in Plant-Pollinator Networks by Using Hierarchical Models That Incorporate Pollinator Detectability and Plant Traits. \emph{PLOS ONE} \textbf{8}, e69200 (2013).

@@

\leavevmode\hypertarget{ref-kettle2011}{}%
33. Kettle, C. J. \emph{et al.} Ecological Implications of a Flower Size/Number Trade-Off in Tropical Forest Trees. \emph{PLOS ONE} \textbf{6}, e16111 (2011).

@@

\leavevmode\hypertarget{ref-chamberlain2020}{}%
47. Chamberlain, S. \emph{et al.} \emph{Taxize: Taxonomic information from around the web}. (2020).

@@

\leavevmode\hypertarget{ref-abdi2010}{}%
56. Abdi, H. \& Williams, L. J. Principal component analysis. \emph{WIREs Computational Statistics} \textbf{2}, 433--459 (2010).

\leavevmode\hypertarget{ref-ballantyne2015}{}%
57. Ballantyne, G., Baldock, K. C. R. \& Willmer, P. G. Constructing more informative plantPollinator networks: Visitation and pollen deposition networks in a heathland plant community. \emph{Proceedings of the Royal Society B: Biological Sciences} \textbf{282}, 20151130 (2015).

@@

\leavevmode\hypertarget{ref-hung2018}{}%
60. Hung, K.-L. J., Kingston, J. M., Albrecht, M., Holway, D. A. \& Kohn, J. R. The worldwide importance of honey bees as pollinators in natural habitats. \emph{Proceedings of the Royal Society B: Biological Sciences} \textbf{285}, 20172140 (2018).

\leavevmode\hypertarget{ref-burkner2017}{}%
61. Bürkner, P.-C. Brms: An R package for Bayesian multilevel models using Stan. \emph{Journal of statistical software} \textbf{80}, 1--28 (2017).

\leavevmode\hypertarget{ref-gabry2019}{}%
62. Gabry, J., Simpson, D., Vehtari, A., Betancourt, M. \& Gelman, A. Visualization in Bayesian workflow. \emph{Journal of the Royal Statistical Society: Series A (Statistics in Society)} \textbf{182}, 389--402 (2019).

@@

\leavevmode\hypertarget{ref-bluthgen2006}{}%
64. Blüthgen, N., Menzel, F. \& Blüthgen, N. Measuring specialization in species interaction networks. \emph{BMC Ecology} \textbf{6}, 9 (2006).

>>>>

\leavevmode\hypertarget{ref-tur2013}{}%
14. Tur, C., Castro-Urgal, R. \& Traveset, A. Linking Plant Specialization to Dependence in Interactions for Seed Set in Pollination Networks. \emph{PLoS One} \textbf{8}, e78294 (2013).

@@

\leavevmode\hypertarget{ref-barrett2003}{}%
23. Barrett, S. C. H. Mating strategies in flowering plants: The outcrossing-selfing paradigm and beyond. \emph{Philos. Trans. R. Soc. Lond. B Biol. Sci.} \textbf{358}, 991--1004 (2003).

@@

\leavevmode\hypertarget{ref-bartomeus2013}{}%
27. Bartomeus, I. Understanding Linkage Rules in Plant-Pollinator Networks by Using Hierarchical Models That Incorporate Pollinator Detectability and Plant Traits. \emph{PLoS One} \textbf{8}, e69200 (2013).

@@

\leavevmode\hypertarget{ref-kettle2011}{}%
33. Kettle, C. J. \emph{et al.} Ecological Implications of a Flower Size/Number Trade-Off in Tropical Forest Trees. \emph{PLoS One} \textbf{6}, e16111 (2011).

@@

\leavevmode\hypertarget{ref-chamberlain2020}{}%
47. Chamberlain, S. \emph{et al.} \emph{Taxize: Taxonomic information from around the web. R package version 0.9.99}. (2020).

@@

\leavevmode\hypertarget{ref-abdi2010}{}%
56. Abdi, H. \& Williams, L. J. Principal component analysis. \emph{WIREs Comp. Stats.} \textbf{2}, 433--459 (2010).

\leavevmode\hypertarget{ref-ballantyne2015}{}%
57. Ballantyne, G., Baldock, K. C. R. \& Willmer, P. G. Constructing more informative plantPollinator networks: Visitation and pollen deposition networks in a heathland plant community. \emph{Proc. Royal Soc. B} \textbf{282}, 20151130 (2015).

@@

\leavevmode\hypertarget{ref-hung2018}{}%
60. Hung, K.-L. J., Kingston, J. M., Albrecht, M., Holway, D. A. \& Kohn, J. R. The worldwide importance of honey bees as pollinators in natural habitats. \emph{Proc. Royal Soc. B} \textbf{285}, 20172140 (2018).

\leavevmode\hypertarget{ref-burkner2017}{}%
61. Bürkner, P.-C. Brms: An R package for Bayesian multilevel models using Stan. \emph{J. Stat. Softw.} \textbf{80}, 1--28 (2017).

\leavevmode\hypertarget{ref-gabry2019}{}%
62. Gabry, J., Simpson, D., Vehtari, A., Betancourt, M. \& Gelman, A. Visualization in Bayesian workflow. \emph{J. R. Stat. Soc. Ser. A Stat. Soc.} \textbf{182}, 389--402 (2019).

@@

\leavevmode\hypertarget{ref-bluthgen2006}{}%
64. Blüthgen, N., Menzel, F. \& Blüthgen, N. Measuring specialization in species interaction networks. \emph{BMC Ecol.} \textbf{6}, 9 (2006).
